---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bis620.2022

<!-- badges: start -->
[![R-CMD-check](https://github.com/Lizwwwwwww/bis620.2022/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Lizwwwwwww/bis620.2022/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of bis620.2022 is to generate time series plot and spectral signature plot from the UKBiobank accelerometry data.

## Installation

You can install the development version of bis620.2022 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Lizwwwwwww/bis620.2022")
```

## Example
This is a basic example which shows you how to use the `accel_plot()` function to draw a time series plot of `X`, `Y` and `Z` in the UKBiobank accelerometry data:

```{r example}
library(bis620.2022)
library(lubridate)
library(ggplot2)

data(ukb_accel)

dt <- dplyr::first(ukb_accel$time)

ukb_accel |>
 # filter(time >= dt  & time < dt + minutes(5)) |>
  accel_plot() +
    theme_minimal() +
    xlab("Time") +
    ylab("Acceleration (in gravities)")
```
This is a basic example which shows you how to use the `spectral_signature()` function to get the spectral signature of accelerometry data: 

The value of `take_log` decides whether the spectral signature is calculated by taking the modulus of the Fourier coefficients of the signal, its default value is `TRUE`.

The value of `inverse` decides whether should the unnormalized inverse transform is computed, its default value is `TRUE`.
```{r example2}
library(bis620.2022)
library(lubridate)
library(ggplot2)

data(ukb_accel)

dt <- dplyr::first(ukb_accel$time)

ukb_accel |>
#  filter(time >= dt & time < dt + minutes(5)) |>
  spectral_signature(take_log = TRUE, inverse = TRUE) |>
  accel_plot()
```
The value of `take_log` decides whether the spectral signature is calculated by taking the modulus of the Fourier coefficients of the signal, its default value is `TRUE`.


[![Code Coverage Page](https://github.com/Lizwwwwwww/bis620.2022/actions/workflows/test-coverage.yaml)](https://github.com/Lizwwwwwww/bis620.2022/actions/workflows/test-coverage.yaml)

[![Lint Result](https://github.com/Lizwwwwwww/bis620.2022/actions/workflows/lint.yaml)](https://github.com/Lizwwwwwww/bis620.2022/actions/workflows/lint.yaml)
